### 2015-12-03 ch05-initvals/InitialValuesPaper.tex
Fix pgfplots external + crossref nastiness
Set up glossaries
Improve initvals chapter: flowgraph font
Patching up some references
Some formatting (minor)

\setlength\onecolumnwidth{0.75\columnwidth}

@@

\tikzset{external/export=false}
\section{Introduction}\label{se:introd}

@@

\begin{figure}
  \centering
  \includegraphics
  [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using BTLS and GTLS starting values, and the novel methods outlined in this paper (3, 4).
  The flow of non-parametric data is depicted by full arrows, with the FRF data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
\end{figure}

The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the MLE optimization process in the parametric identification of each system. 
The requisite procedures for the estimators are as follows, from left to right of the flowchart in \figref{fig:flowgraph}:

@@

The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the MLE.

@@

The Generalized Total Least Squares (GTLS) and the Bootstrapped Total Least Squares (BTLS) have been discussed in \citep{pintGuil1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior is suitable for improvement by the FRF smoothing tools, described below.

@@

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows \citep{Lumori2014}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact FRF $G_0$ and the transient term
%the leakage 
$T$ 
%from transients 
allow for an optimal application of the LPM, leading to a smooth FRF estimate with the transient suppressed.
%the elimination of both the leakage and interpolation errors.

  With reference to a detailed discussion in~\citep{Lumori2014}, the LPM utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

  The LPM estimate of the FRF at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

@@

\item
\emph{Regularized finite impulse response (RFIR)}

%\ML: {This is included for comparison purposes .....}
The regularized finite impulse response (RFIR) method is a special case of the regularized autoregressive exogenous (RARX) method. 
%This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.

%\JL{
The RFIR estimator is formulated in the time domain. It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
In this paper, the Diagonal Correlated (DC) kernel is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the log marginal likelihood (LML) of the measured output signal:
\begin{align}
\text{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \texttt{fmincon} in \MATLAB.

An implementation of the RFIR estimator is available as the \texttt{arx} function in the System Identification Toolbox since \MATLAB 2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \texttt{arxoptions}. 
The hyperparameters can be determined via \texttt{arxregul}.
More information about the RFIR estimator can be found in
~\citep{Pillonetto201081,Chen20121525}. 
The DFT of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

%\JL{
%{remark}
%\label{rem:FRFasSpectrum}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the FRF. A corresponding parametric estimate is obtained as follows. A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be 1 at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero. It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data. This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
%\end{remark}
%}

@@

The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
\begin{align}
\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \texttt{integral}.
%\comment{EG: The exact implementation is in the L2Norm function. Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr. testDistance). I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \texttt{binofit}).
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.

@@

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \texttt{AO} and \texttt{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the inverse DFT.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
%  \input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\section{Remark on Generality}
\label{se:Generality}
In the previous sections, the usefulness of smoothing techniques to obtain initial values has been illustrated on example systems.
Other systems, e.g. discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} commands in \MATLAB{} have also been tried.

@@

>>>>

\setlength\onecolumnwidth{\columnwidth}

@@

\section{Introduction}\label{se:introd}

@@

\begin{figure}
  \centering
  \includegraphics
  [width=0.95\onecolumnwidth]{\thisDir/fig/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: (1) an approach using the true model as initial estimate; (2) an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel methods outlined in this paper (3, 4).
  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} \label{fig:flowgraph}
\end{figure}

The ultimate aim is to find initial estimates that are good enough to steer clear of the local optima during the \gls{MLE} optimization process in the parametric identification of each system. 
The requisite procedures for the estimators are as follows, from left to right of the flowchart in \figref{fig:flowgraph}:

@@

The estimates from this procedure are for comparison purposes with those from the other procedures. They will be crucial to the computation of the global optimum of the \gls{MLE}.

@@

The \gls{GTLS} and the \gls{BTLS} have been discussed in \citep{pintGuil1998}. These are modifications of equation \eqref{eq:MLEcf}, which still take into account the noise information while retaining the quadratic nature w.r.t. $\theta$. 
These estimators preserve consistency, such that the estimates converge asymptotically to the true parameters for $N\to\infty$. 
Their finite sample behavior, however, is suitable for improvement by the \gls{FRF} smoothing tools as described below.

@@

A reliably good estimate of the FRF of the chosen system can be obtained via the LPM, which is summarized as follows~\citep{Lumori2014}. Formulated as a nonparametric linear-least-squares-estimate, the LPM is first applied to estimate the FRF from a full data record of a SISO system, systematically expressed in an output-error framework, shown in \figref{fig:oesetup}. The smooth characteristics of both the exact \gls{FRF} $G_0$ and the transient term $T$ allow for an optimal application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient suppressed.

  With reference to a detailed discussion in~\citep{Lumori2014}, the \gls{LPM} utilizes the following quadratic local polynomials to approximate (in least squares sense) and, thus, smooth $G_0$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
G_0(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in\mathbb{W}_n,\quad$$\mathbb{W}_n = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. In this paper, $n=3$.

  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

@@

\item \emph{\Glsfirst{RFIR}}

The \gls{RFIR} method is a special case of the \gls{RARX} method. 
%This is a well known method which is included in this paper for comparison purposes with the smooth LPM and with other existing estimators.

%\JL{
The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$ and $\beta$ are determined using Empirical Bayes, i.e. as the maximizers of the \gls{LML} of the measured output signal:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta)^{-1}y - \log |\Sigma(\alpha,\beta)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \code{fmincon} in \MATLAB.

An implementation of the \gls{RFIR} estimator is available as the \code{arx} function in the System Identification Toolbox since \MATLAB~2013b with $\mathtt{na} = 0$, $\mathtt{nb} = n_g$, $\mathtt{nk}=0$ and regularization enabled in \code{arxoptions}. 
The hyperparameters can be determined via \code{arxregul}.
More information about the \gls{RFIR} estimator can be found in
~\citep{Pillonetto201081,Chen20121525}. 
The \gls{DFT} of the obtained regularized estimate of the impulse response $\hat g_{\mathrm{RFIR}}$ of the system yields a smoothed estimate of the FRF.
%\JL{Having obtained a regularized estimate of the impulse response of the system, its DFT (Discrete Fourier Transform) yields an estimate of the FRF.}
\end{enumerate}

\begin{remark}
Note that methods 3) and 4) result in a non-parametric estimate of the transfer function, represented as the \gls{FRF}. 
A corresponding parametric estimate is obtained as follows. 
A parametric estimator (GTLS, BTLS, and MLE) is invoked, where the input spectrum is considered to be $1$ at all frequencies (Dirac in the time domain), and the output spectrum is set equal to the estimated FRF, with the transient term $I$ set to zero. It is important to note that invoking the GTLS, BTLS and MLE on the FRFs from methods 3) and 4) will yield a different result from applying the GTLS, BTLS and MLE on the raw data. This is because the FRFs from 3) and 4) have been smoothed and, thus, have a significantly lower noise variance.
\end{remark}
%}

@@

The distance measure used in equation \eqref{eq:successrateTol} is defined, for discrete time, as
\begin{align}
\|G\|_2 = \sqrt{\frac{1}{2\pi}\int_0^{2\pi} |G(e^{-j\omega})|^2\ \mathrm{d}\omega}
\end{align}
 which, in practice, is computed by using the adaptive global quadrature algorithm provided by the MATLAB function \code{integral}.
%\comment{EG: The exact implementation is in the L2Norm function. Basically, either numerical or symbolic integration can be used (as our models are parametric), but both yield equally workable results (cfr. testDistance). I picked a full numerical approach as the symbolic one doesn't always work on my computer.}
%\JL{The success rate in \eqref{eq:successrateTol} will be estimated via Monte Carlo simulations, further\ML{/later} on.}
The success rate in equation \eqref{eq:successrateTol} is estimated via Monte Carlo simulations in  Section \ref{se:CompuSR}.

@@

In \figref{fig:successRateVS_SNR36N3dB}, the success rate (and its $95\%$ confidence interval) obtained from the Monte Carlo simulations is shown to compare the proposed method with previously existing approaches.
The confidence intervals are calculated via the Clopper-Pearson method~\citep{Clopper1934} (as implemented in \MATLAB's \code{binofit}).
This is known to yield somewhat conservative bounds, especially if only failures or successes are observed~\citep{Ross2003}.
Consequently, the improvements observed in \figref{fig:successRateVS_SNR36N3dB} underestimate the actual improvement slightly.

@@

To measure the transfer function, the \BK{} 1613 Filter was excited by a signal $r(t)$ and both its input $u(t)$ and output $y(t)$ were measured as shown in \figref{fig:measurementSetup}.
The output $y(t)$, however, was disturbed by a noise generator that added white noise over the frequency range $[\mathrm{DC}, 20\unit{kHz}]$.
The excitation signal $r(t)$ was white random noise with a standard deviation $\sigma_r = 0.25 \unit{V}$, consisting of $N_S = 8\,192$ samples, and sampled at $92 \unit{kHz}$.
The same noise sequence was repeated $N_R = 100$ times in succession, such that a non-parametric estimate of the noise could be obtained and the performance of the methods could be gauged over these different repetitions.
To distinguish the different repetitions, we denote the $r^{\text{th}}$ repetition of the $u$ signal as $u^{[r]}(t)$ (and similarly for $y(t)$).
The signal generation and acquisition was by means of a National Instruments Elvis II, using the respective \code{AO} and \code{AI} pins on the breadboard, which were wired to BNC connectors.
Although acquisition and generation were synchronized, there was a small delay $\tau = 9\unit{\mu s}$ between the acquisition of the input $u(t)$ and the output $y(t)$.
The output spectrum $Y(\omega)$ was multiplied by $\exp\left(-j\omega\tau \right)$ such that the delay-compensated $y(t)$ could be obtained using the inverse DFT.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  %\input{\thisDir/fig/bode-bk1613.tikz} %TODO: re-enable figure and make less dense
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\onecolumnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  %\input{\thisDir/fig/elvis-spectra.tikz}
  %TODO: simplify figure
  \caption[Measured input/output spectra of \BK{} filter.]{Input $U^{[r]}(\omega)$ and output $Y^{[r]}(\omega)$ spectra~\legref[2]{leg:SpectraMeasurement:U:single} measured using the Elvis.
  \legref[2]{leg:SpectraMeasurement:U:mean}: the mean spectra $\tilde{U}$ and $\tilde{Y}$, \legref[2]{leg:SpectraMeasurement:U:noise}: noise levels $\hat\sigma_U$ and $\hat\sigma_Y$.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\section{Remark on Generality}
\label{se:Generality}
In the previous sections, the usefulness of smoothing techniques to obtain initial values has been illustrated on example systems.
Other systems, e.g. discrete-time low-pass, high-pass, band-pass and band-stop filters of tenth order generated by the \code{cheby1}, \code{cheby2}, \code{ellip} and \code{butter} commands in \MATLAB{} have also been tried.

@@

\TODO{figures from review letter}

### 2015-12-03 config/glossaries.inc.tex
Example: numerical precision -> period
Some formatting (minor)

@@

\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}

@@

%% ACRONYMS
\newacronym{BLA}{BLA}{best linear approximation}

@@

\newacronym{DC}{DC}{direct current}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

@@

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}

\newacronym{MIMO}{MIMO}{multiple-input multiple-output}
\newacronym{MISO}{MISO}{multiple-input single-output}
\newacronym{MSE}{MSE}{mean squared error}

@@

\newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}
\newacronym{RMS}{RMS}{root-mean-square}
\newacronym{RMSE}{RMSE}{root mean squared error}

>>>>

\newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}

@@

@@

%% ACRONYMS
\newacronym{BLA}{BLA}{best linear approximation}
\newacronym{BTLS}{BTLS}{bootstrapped total least squares}

@@

\newacronym{DC}{DC}{direct current}
\newacronym{DCkernel}{DC kernel}{Diagonal Correlated (DC) kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{GTLS}{GTLS}{generalized total least squares}

@@

\newacronym{LML}{LML}{log marginal likelihood}
\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LS}{LS}{least-squares}
\newacronym{LTI}{LTI}{linear time-invariant}

\newacronym{MIMO}{MIMO}{multiple-input multiple-output}
\newacronym{MISO}{MISO}{multiple-input single-output}
\newacronym{MLE}{MLE}{maximum-likelihood estimator}
\newacronym{MSE}{MSE}{mean squared error}

@@

\newacronym{RARX}{RARX}{regularized auto-regressive exogenous}
\newacronym{RFIR}{RFIR}{regularized finite impulse response}
\newacronym{RMS}{RMS}{root-mean-square}
\newacronym{RMSE}{RMSE}{root mean squared error}
